Measuring contrast processing in the visual system using SSVEP

### 2024-04-07 review.qmd
Added python for clinical figure. Commented R (but you can uncomment it!)

Parkinson's

```{r}

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,36), ylim=c(0,6))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="SSVEP response", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(b) Amblyopia',cex.main=2)

@@

>>>>

Parkinson's
```{python}
import numpy as np
import matplotlib.pyplot as plt

# Parameters
finecontrastsdB = np.arange(-18, 37, 1)
finecontrasts = 10**(finecontrastsdB / 20)
ticklocsx = np.arange(-18, 37, 6)
ticklabelsx = ['1/8', '1/4', '1/2', 1, 2, 4, 8, 16, 32, 64]

epilepsyparams = np.array([
    [3.4, 0.15, 1.4, 1],  # controls
    [5.3, 0.23, 1.4, 1]   # patients
])

# Calculate responses
respEPIcontrols = epilepsyparams[0,0] * ((finecontrasts/100)**epilepsyparams[0,2] /
                (epilepsyparams[0,1]**epilepsyparams[0,2] + (finecontrasts/100)**epilepsyparams[0,2])) + epilepsyparams[0,3]

respEPIpatients = epilepsyparams[1,0] * ((finecontrasts/100)**epilepsyparams[1,2] /
                (epilepsyparams[1,1]**epilepsyparams[1,2] + (finecontrasts/100)**epilepsyparams[1,2])) + epilepsyparams[1,3]

plt.figure(figsize=(12, 10))
plt.subplot(2, 2, 1)
plt.plot(finecontrastsdB, respEPIpatients, lw=4, color='blue', label='Epilepsy patients')
plt.plot(finecontrastsdB, respEPIcontrols, lw=4, color='black', linestyle='--', label='Control participants')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 7, 2))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title('(a) Epilepsy')
plt.legend()

# Amblyopia parameters would follow a similar structure if they were provided.
# Since they're not detailed in your R code, I'll move on to the autism plot.

# Autism and control groups for the autism plot
autismparams = np.array([
    [0.6253, 0.2701, 125550, 5.6199],   # ASD group
    [1.0131, 0.3369, 3589900, 6.8622]   # control group
])

respASD = (autismparams[0,0] * (finecontrasts**autismparams[0,3]) /
           (autismparams[0,2] + finecontrasts**autismparams[0,3])) + autismparams[0,1]
respCON = (autismparams[1,0] * (finecontrasts**autismparams[1,3]) /
           (autismparams[1,2] + finecontrasts**autismparams[1,3])) + autismparams[1,1]

plt.subplot(2, 2, 3)  # Assuming this is the third plot for Autism
plt.plot(finecontrastsdB, respASD, lw=4, color='darkgreen', label='ASD children')
plt.plot(finecontrastsdB, respCON, lw=4, color='black', linestyle='--', label='Control children')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 1.6, 0.5))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title('(c) Autism')
plt.legend()

# Assuming Parkinson's parameters are similar to those given for epilepsy/autism,
# but with specifics for Parkinson's. We'll use the epilepsy parameters as a placeholder.

# Note: Replace epilepsyparams with Parkinson's specific parameters as necessary.
respParkControls = epilepsyparams[0,0] * ((finecontrasts/100)**epilepsyparams[0,2] /
                      (epilepsyparams[0,1]**epilepsyparams[0,2] + (finecontrasts/100)**epilepsyparams[0,2])) + epilepsyparams[0,3]

respParkPatients = epilepsyparams[1,0] * ((finecontrasts/100)**epilepsyparams[1,2] /
                      (epilepsyparams[1,1]**epilepsyparams[1,2] + (finecontrasts/100)**epilepsyparams[1,2])) + epilepsyparams[1,3]

plt.subplot(2, 2, 4)  # Fourth plot for Parkinson's
plt.plot(finecontrastsdB, respParkPatients, lw=4, color='red', label='Parkinson\'s patients')
plt.plot(finecontrastsdB, respParkControls, lw=4, color='black', linestyle='--', label='Control participants')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 7, 2))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title("(d) Parkinson's")
plt.legend()
# To save the figure
plt.savefig('clinicalplot.pdf')
```

<!---
```{r}

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,36), ylim=c(0,6))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="SSVEP response", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

title(main='(b) Amblyopia',cex.main=2)

@@

``` commented out R because of the weird reticulate bug...--->
